---
title: "Correlation with the ProCan-DepMapSanger dataset"
author: Beata Szeitz
output:
  html_notebook:
    toc: yes
---

# Load packages and functions

```{r }
# R vs.4.2.0
source("Load_packages.R")
source("Utility_functions.R")
source("Color_list.R")
```


# Search for commonly measured cell lines

Read in and clean sample info:

```{r }
ProCan.Annot <- read.xlsx("Files/DepMap/Goncalves_2022_TableS2.xlsx",2)
colnames(ProCan.Annot) <- ProCan.Annot[1,]
ProCan.Annot <- ProCan.Annot[-1,]

ProCan.Annot <- ProCan.Annot[ProCan.Annot$Cancer_type =="Small Cell Lung Carcinoma",]
```

Search for commonly present cell lines in both study:

```{r }
Annot <- read_in_with_rowname("Files/Annotation",F)
row.names(Annot) <- Annot$Sample

Annot$Cell_line <- Annot$Sample

Annot$Cell_line <- ifelse(startsWith(Annot$Cell_line,"H"), paste("NCI",Annot$Cell_line,sep="-"), Annot$Cell_line)
Annot$Cell_line <- ifelse(Annot$Cell_line =="CRL2177", "SW1271", Annot$Cell_line)
Annot$Cell_line <- ifelse(Annot$Cell_line =="CRL2066", "DMS114", Annot$Cell_line)
Annot$Cell_line <- ifelse(Annot$Cell_line =="DMS53", "DMS-53", Annot$Cell_line)
Annot$Cell_line <- ifelse(Annot$Cell_line =="DMS153", "DMS-153", Annot$Cell_line)
Annot$Cell_line <- ifelse(Annot$Cell_line =="DMS114", "DMS-114", Annot$Cell_line)
Annot$Cell_line <- ifelse(Annot$Cell_line =="SHP77", "SHP-77", Annot$Cell_line)
Annot$Cell_line <- ifelse(Annot$Cell_line =="CORL311", "COR-L311", Annot$Cell_line)

Annot$Cell_line[!Annot$Cell_line %in% ProCan.Annot$Cell_line]

ProCan.Annot.common <- ProCan.Annot[ProCan.Annot$Cell_line %in% Annot$Cell_line,]

for (i in 1:nrow(ProCan.Annot.common)){
  ProCan.Annot.common$Sample[i] <- Annot[Annot$Cell_line == ProCan.Annot.common$Cell_line[i],"Sample"]
}

Annot.common <- Annot[Annot$Cell_line %in% ProCan.Annot.common$Cell_line,]

```

8 cell lines were not included in the ProCan study: H841 (Y), GLC4 (A), HLHE (Y), DMS153 (A), H378 (A), H1882 (A), N417 (N), H372 (Y)

# Search for commonly quantified proteins

Read in and clean protein expression table:


```{r }
ProCan.Expr <- read.xlsx("Files/DepMap/Goncalves_2022_TableS3.xlsx",1)
colnames(ProCan.Expr) <- ProCan.Expr[1,]
ProCan.Expr <- ProCan.Expr[-1,]
row.names(ProCan.Expr) <- ProCan.Expr[,1]
ProCan.Expr <- ProCan.Expr[,-1]

ProCan.Expr.common <- as.data.frame(t(ProCan.Expr[ProCan.Annot.common$Project_Identifier,]))

for (i in 1:ncol(ProCan.Expr.common)){
  colnames(ProCan.Expr.common)[i] <- ProCan.Annot.common[ProCan.Annot.common$Project_Identifier == colnames(ProCan.Expr.common)[i], "Sample"]
}

row.names(ProCan.Expr.common) <- sapply(strsplit(row.names(ProCan.Expr.common), split=";"), "[[",1)
ProCan.Expr.common <- filter_missingvalues(ProCan.Expr.common, 1)


```



7916 and 5255 common proteins quantified in both studies in the cell pellet and media, respectively

```{r }
CP.expr <- read_in_with_rowname("Files/CP_expression_full",F)[,Annot.common$Sample]
CP.expr <- filter_missingvalues(CP.expr, 1)

common.proteins <- intersect(row.names(CP.expr), row.names(ProCan.Expr.common))

ProCan.Expr.common.common <- ProCan.Expr.common[common.proteins,]
CP.expr.commmon <- CP.expr[common.proteins,colnames(ProCan.Expr.common.common)]


CM.expr <- read_in_with_rowname("Files/CM_expression_full",F)[,Annot.common$Sample]
CM.expr <- filter_missingvalues(CM.expr, 1)
ProCan.Expr.common.secr <- filter_missingvalues(ProCan.Expr.common[row.names(ProCan.Expr.common) %in% row.names(CM.expr),],1)

common.proteins.cm <- intersect(row.names(CM.expr), row.names(ProCan.Expr.common.secr))

CM.expr.common <- CM.expr[common.proteins.cm,]
ProCan.Expr.common.CM <- ProCan.Expr.common[common.proteins.cm,]


```


ProCan data is already normalized

```{r Sample histograms, fig.width = 15, fig.height = 5}
plot_sample_histograms(ProCan.Expr.common.common, "ProCan", "After loading") 
```




# Correlation between protein abundances (min.80% pairwise complete obs)


```{r }
Corr.anal.res.CP <- data.frame(Protein = row.names(ProCan.Expr.common.common),
                            Nr.common.obs = NA,
                            Corr.coeff = NA,
                            Corr.pvalue = NA,
                            Lwr.CI = NA,
                            Upr.CI = NA,
                            t = NA,
                            df = NA)
Corr.anal.res.CM <- data.frame(Protein = row.names(ProCan.Expr.common.CM),
                            Nr.common.obs = NA,
                            Corr.coeff = NA,
                            Corr.pvalue = NA,
                            Lwr.CI = NA,
                            Upr.CI = NA,
                            t = NA,
                            df = NA)
Corr.anal.res.random <- Corr.anal.res.CP
Corr.anal.res.random.secr <- Corr.anal.res.CM


i=1
for (i in 1:nrow(Corr.anal.res.CP)){
  merged.df <- data.frame(ProCan = as.numeric(ProCan.Expr.common.common[i,]),
                       Own = as.numeric(CP.expr.commmon[i,]))
  nr.obs <- nrow(na.omit(merged.df))
  if (nr.obs < 15){
    Corr.anal.res.CP[i,2:8] <- NA
    next
  }
  corres <- cor.test(merged.df$ProCan, merged.df$Own, use="pairwise.complete.obs", method = "pearson")
  Corr.anal.res.CP[i,2:8] <- paste(c(nr.obs, corres$estimate, corres$p.value, corres$conf.int[1], corres$conf.int[2], corres$statistic, corres$parameter))
}
Corr.anal.res.CP[2:8] <- sapply(Corr.anal.res.CP[2:8], as.numeric)
Corr.anal.res.CP$Corr.FDR <- p.adjust(Corr.anal.res.CP$Corr.pvalue, "BH")


for (i in 1:nrow(Corr.anal.res.CM)){
  merged.df <- data.frame(ProCan = as.numeric(ProCan.Expr.common.CM[i,]),
                       Own = as.numeric(CM.expr.common[i,]))
  nr.obs <- nrow(na.omit(merged.df))
  if (nr.obs < 15){
    Corr.anal.res.CM[i,2:8] <- NA
    next
  }
  corres <- cor.test(merged.df$ProCan, merged.df$Own, use="pairwise.complete.obs", method = "pearson")
  Corr.anal.res.CM[i,2:8] <- paste(c(nr.obs, corres$estimate, corres$p.value, corres$conf.int[1], corres$conf.int[2], corres$statistic, corres$parameter))
}
Corr.anal.res.CM[2:8] <- sapply(Corr.anal.res.CM[2:8], as.numeric)
Corr.anal.res.CM$Corr.FDR <- p.adjust(Corr.anal.res.CM$Corr.pvalue, "BH")


seeds <- seq(1,nrow(Corr.anal.res.random))
i=1
for (i in 1:nrow(Corr.anal.res.random)){
  set.seed(seeds[i])
  random.order <- sample(ncol(ProCan.Expr.common.common))
  merged.df <- data.frame(ProCan = as.numeric(ProCan.Expr.common.common[i,]),
                       Own = as.numeric(CP.expr.commmon[i,random.order]))
  nr.obs <- nrow(na.omit(merged.df))
  if (nr.obs < 15){
    Corr.anal.res.random[i,2:8] <- NA
    next
  }
  corres <- cor.test(merged.df$ProCan, merged.df$Own, use="pairwise.complete.obs", method = "pearson")
  Corr.anal.res.random[i,2:8] <- paste(c(nr.obs, corres$estimate, corres$p.value, corres$conf.int[1], corres$conf.int[2], corres$statistic, corres$parameter))
}
Corr.anal.res.random[2:8] <- sapply(Corr.anal.res.random[2:8], as.numeric)
Corr.anal.res.random$Corr.FDR <- p.adjust(Corr.anal.res.random$Corr.pvalue, "BH")



seeds <- seq(1,nrow(Corr.anal.res.random.secr))
i=1
for (i in 1:nrow(Corr.anal.res.random.secr)){
  set.seed(seeds[i])
  random.order <- sample(ncol(ProCan.Expr.common.common))
  merged.df <- data.frame(ProCan = as.numeric(ProCan.Expr.common.common[i,]),
                       Own = as.numeric(CP.expr.commmon[i,random.order]))
  nr.obs <- nrow(na.omit(merged.df))
  if (nr.obs < 15){
    Corr.anal.res.random.secr[i,2:8] <- NA
    next
  }
  corres <- cor.test(merged.df$ProCan, merged.df$Own, use="pairwise.complete.obs", method = "pearson")
  Corr.anal.res.random.secr[i,2:8] <- paste(c(nr.obs, corres$estimate, corres$p.value, corres$conf.int[1], corres$conf.int[2], corres$statistic, corres$parameter))
}
Corr.anal.res.random.secr[2:8] <- sapply(Corr.anal.res.random.secr[2:8], as.numeric)
Corr.anal.res.random.secr$Corr.FDR <- p.adjust(Corr.anal.res.random.secr$Corr.pvalue, "BH")

```




```{r }
quantile(Corr.anal.res.CP$Corr.coeff, na.rm=TRUE)
quantile(Corr.anal.res.CM$Corr.coeff, na.rm=TRUE)
quantile(Corr.anal.res.random$Corr.coeff, na.rm=TRUE)

```

Random indicates the protein expression correlation between randomly shuffled samples.

```{r }
density.DF <- na.omit(data.frame(Protein = c(Corr.anal.res.CP$Protein, Corr.anal.res.CM$Protein, Corr.anal.res.random$Protein),
                         Corr.coef = c(Corr.anal.res.CP$Corr.coeff, Corr.anal.res.CM$Corr.coeff,Corr.anal.res.random$Corr.coeff),
                         Data = c(rep("Matched.CP", nrow(Corr.anal.res.CP)), 
                                  rep("Matched.CM", nrow(Corr.anal.res.CM)),
                                  rep("Random", nrow(Corr.anal.res.random)))))
ggplot(density.DF, aes(x=Corr.coef, fill=Data)) +
  geom_histogram(alpha=0.7,color="black",aes(y = ..density..))

```

## Density plots


Correlation with CP data is good (but not that good with CM data)

```{r , fig.width=8, fig.height=3}
density.DF <- na.omit(data.frame(Protein = c(Corr.anal.res.CP$Protein,
                                             Corr.anal.res.CM$Protein, 
                                             Corr.anal.res.random$Protein,
                                             Corr.anal.res.random.secr$Protein),
                         Corr.coef = c(Corr.anal.res.CP$Corr.coeff, 
                                       Corr.anal.res.CM$Corr.coeff,
                                       Corr.anal.res.random$Corr.coeff,
                                       Corr.anal.res.random.secr$Corr.coeff),
                         Data = c(rep("Matched.CP", nrow(Corr.anal.res.CP)), 
                                  rep("Matched.CM", nrow(Corr.anal.res.CM)),
                                  rep("Random.CP", nrow(Corr.anal.res.random)),
                                  rep("Random.CM", nrow(Corr.anal.res.random.secr))),
                         `Data type` = c(rep("Corr. btw. matched samples", nrow(Corr.anal.res.CP)), 
                                       rep("Corr. btw. matched samples", nrow(Corr.anal.res.CM)),
                                       rep("Corr. btw. randomly shuffled samples", nrow(Corr.anal.res.random)),
                                       rep("Corr. btw. randomly shuffled samples", nrow(Corr.anal.res.random.secr))),
                         check.names = FALSE))
g1 <- ggplot(density.DF[grepl("CP",density.DF$Data),], aes(x=Corr.coef, fill=`Data type`)) +
  geom_density(alpha=0.4)+
    theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
g2 <- ggplot(density.DF[grepl("CM",density.DF$Data),], aes(x=Corr.coef, fill=`Data type`)) +
  geom_density(alpha=0.4)+
    theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
ggarrange(g1, g2, common.legend = TRUE)

```


```{r , fig.width=5, fig.height=3}
g1 + xlab("Pearson's r") + ylab("Density")
ggsave(g1 + xlab("Pearson's r") + ylab("Density"), file="Figures/Correlation_btw_ProCan_and_ours.png")

```





