---
title: "Proteomic data preprocessing"
author: Beata Szeitz
output:
  html_notebook:
    toc: yes
---



# Load functions and files


```{r Load packages}
.packages = c("ggplot2","ggbiplot","ggplotify", "ggpubr","lme4", "circlize","ComplexHeatmap", "patchwork","pvca","Biobase")
lapply(.packages, require, character.only=TRUE)
source("Utility_functions.R")
source("Color_list.R")
```




```{r Load expression tables}
CP.raw <- read_in_Perseus("Files/SCLC_CP_raw.txt", inj.order = F)
CM.raw <- read_in_Perseus("Files/SCLC_CM_raw.txt", inj.order = F)
# in both cases, protein info was already added, as well as Gene name was extracted from the "Description" column

```


```{r Load annotations}
Annot <- read.delim("Files/Proteomics_Cell_line_annotation.txt", check.names = F) #  Annotation table where qPCR values are already min-max-scaled

colnames(CP.raw[[2]])[grep("Sample", colnames(CP.raw[[2]]))] <- "Sample"
colnames(CM.raw[[2]])[grep("Sample", colnames(CM.raw[[2]]))] <- "Sample"

CP.raw[[2]]$Sample <- ifelse(CP.raw[[2]]$Sample =="COR", "CORL311", CP.raw[[2]]$Sample)
CM.raw[[2]]$Sample <- ifelse(CM.raw[[2]]$Sample =="COR", "CORL311", CM.raw[[2]]$Sample)

```

COR was renamed to CORL311.



```{r Create list of tables}

Tables <- list(CP = list(Expr.raw = CP.raw[[1]],
                         Annot = merge(CP.raw[[2]][,c("Sample", "MainID", "Replicate", "MSbatch")], Annot, by="Sample", all.x=T,sort =F),
                         Info =CP.raw[[3]]),
               CM = list(Expr.raw = CM.raw[[1]],
                         Annot = merge(CM.raw[[2]][,c("Sample", "MainID", "Replicate", "MSbatch")], Annot, by="Sample", all.x=T,sort =F),
                         Info = CM.raw[[3]]))
row.names(Tables$CP$Annot) <- Tables$CP$Annot$MainID
row.names(Tables$CM$Annot) <- Tables$CM$Annot$MainID
Tables$CP$Annot <- Tables$CP$Annot[colnames(Tables$CP$Expr.raw),]
Tables$CM$Annot <- Tables$CM$Annot[colnames(Tables$CM$Expr.raw),]

Tables$CP$Annot$Data.Acquisiton <- ifelse(grepl("DDA",Tables$CP$Annot$MainID), "DDA", "DIA")
Tables$CM$Annot$Data.Acquisiton <- ifelse(grepl("DDA",Tables$CM$Annot$MainID), "DDA", "DIA")

```


Removal of measurements: 1st DDA for SCLC20,26,29 in CP data (these were repeated)
And SCLC08 from batch1 in CM

```{r Removal measurements before normalization}
to.remove.CP <- c("SCLC20_DDA_R1", "SCLC26_DDA_R1", "SCLC29_DDA_R1")
to.remove.CM <- c("SCLC08_B1_DDA_R1")

Tables$CP$Expr.raw <- Tables$CP$Expr.raw[,!colnames(Tables$CP$Expr.raw) %in% to.remove.CP]
Tables$CM$Expr.raw <- Tables$CM$Expr.raw[,!colnames(Tables$CM$Expr.raw) %in% to.remove.CM]

Tables$CP$Annot <- Tables$CP$Annot[!row.names(Tables$CP$Annot) %in% to.remove.CP,]
Tables$CM$Annot <- Tables$CM$Annot[!row.names(Tables$CM$Annot) %in% to.remove.CM,]

```




# Log2 transformation and median normalization


```{r Log2 transform }
Tables$CP$Expr <- as.data.frame(apply(Tables$CP$Expr.raw, 2, log2))
Tables$CM$Expr <- as.data.frame(apply(Tables$CM$Expr.raw, 2, log2))
```

```{r Sample histograms before normalization, fig.width = 15, fig.height = 5}
plot_sample_histograms(Tables$CP$Expr, "SCLC CP", "Before Normalization") + geom_vline(xintercept = grep(2,Tables$CP$Annot$MSbatch)[1]-1, colour="blue", size=1)
plot_sample_histograms(Tables$CM$Expr, "SCLC CM", "Before Normalization") + geom_vline(xintercept = grep(2,Tables$CM$Annot$MSbatch)[1]-1, colour="blue", size=1)
```




```{r Median normalization}
Tables$CP$Expr <- normalize_median(Tables$CP$Expr)
Tables$CM$Expr <- normalize_median(Tables$CM$Expr)
```


```{r Sample histograms after normalization, fig.width = 15, fig.height = 5}
plot_sample_histograms(Tables$CP$Expr, "SCLC CP", "After Median Normalization") + geom_vline(xintercept = grep(2,Tables$CP$Annot$MSbatch)[1]-1, colour="blue", size=1)
plot_sample_histograms(Tables$CM$Expr, "SCLC CM", "After Median Normalization") + geom_vline(xintercept = grep(2,Tables$CM$Annot$MSbatch)[1]-1, colour="blue", size=1)
```







# Examine and merge technical replicates in the same batch


```{r Correlation matrix between technical replicates from the same batch, fig.width=20, fig.height=20}

heatmaps <- list()

for (i in 1:2){
  batch1 <- Tables[[i]]$Annot[Tables[[i]]$Annot$MSbatch ==1,"MainID"]
  batch2 <- Tables[[i]]$Annot[Tables[[i]]$Annot$MSbatch ==2,"MainID"]
   
  col_fun = colorRamp2(c(0.85, 0.90,0.94,0.98, 1), c("lightblue", "white","orange","darkred","black"))
  p1 <- as.ggplot(Heatmap(as.matrix(cor(Tables[[i]]$Expr[,batch1], use="pairwise.complete.obs")), 
          column_title = paste0(names(Tables)[i],"\n  Batch 1 measurements"), 
          col = col_fun,
          row_split = Tables[[i]]$Annot[batch1,"Replicate"], 
          column_split = Tables[[i]]$Annot[batch1,"Replicate"], 
          cluster_row_slices = F, cluster_column_slices = F, row_title = NULL, show_column_names = F))
  p2 <- as.ggplot(Heatmap(as.matrix(cor(Tables[[i]]$Expr[,batch2], use="pairwise.complete.obs")), 
          column_title = paste0(names(Tables)[i],"\n  Batch 2 measurements"), 
          col = col_fun,
          row_split = Tables[[i]]$Annot[batch2,"Replicate"], 
          column_split = Tables[[i]]$Annot[batch2,"Replicate"], 
          cluster_row_slices = F, cluster_column_slices = F, row_title = NULL, show_column_names = F))
  heatmaps[[i]] <- p1+p2
}

heatmaps[[1]] / heatmaps[[2]]

```






The following replicates seem to be outliers in the CP data: SCLC02_B2_DDA_R1 & SCLC08_B2_DIA_R1 & SCLC23_DDA_R1 & SCLC21_DIA_R1, but these were not deleted (because by taking the median of the 3 samples, the outlier replicate should not have large effect on the median protein intensities)


```{r Taking the median of technical replicates, eval=F}

for (i in 1:2){
  batch1 <- Tables[[i]]$Annot[Tables[[i]]$Annot$MSbatch ==1,"MainID"]
  batch2 <- Tables[[i]]$Annot[Tables[[i]]$Annot$MSbatch ==2,"MainID"]
  if (i ==2){
    batch2 <- batch2[batch2!="SCLC09_B2_DDA_R1"]
  }
  batch1.expr.med <- median_of_repeated_measurements(Tables[[i]]$Expr,unique(Tables[[i]]$Annot[batch1,"Replicate"]),"_" )
  colnames(batch1.expr.med) <- paste(colnames(batch1.expr.med), "Batch1", sep="_")
  batch2.expr.med <- median_of_repeated_measurements(Tables[[i]]$Expr,unique(Tables[[i]]$Annot[batch2,"Replicate"]),"_" )
  colnames(batch2.expr.med) <- paste(colnames(batch2.expr.med), "Batch2", sep="_")
  Tables[[i]]$Expr.Med.withinBatch <- merge(batch1.expr.med, batch2.expr.med, by="row.names")
  row.names(Tables[[i]]$Expr.Med.withinBatch) <- Tables[[i]]$Expr.Med.withinBatch$Row.names
  Tables[[i]]$Expr.Med.withinBatch$Row.names <- NULL
  Tables[[i]]$Annot.Med.withinBatch <- Tables[[i]]$Annot[,! colnames(Tables[[i]]$Annot) %in% c("MainID","MSorder", "MSorder.Cat",
                                                                                               "Data.Acquisiton")]
  Tables[[i]]$Annot.Med.withinBatch$MainID <- paste(Tables[[i]]$Annot.Med.withinBatch$Replicate,
                                                    paste0("Batch",Tables[[i]]$Annot.Med.withinBatch$MSbatch),sep="_")
  
  Tables[[i]]$Annot.Med.withinBatch <- unique(Tables[[i]]$Annot.Med.withinBatch)
  row.names(Tables[[i]]$Annot.Med.withinBatch) <- Tables[[i]]$Annot.Med.withinBatch$MainID
}

save(Tables, file="RData/Tables_afterTechReplMerge.RData")

```



```{r }
load("RData/Tables_afterTechReplMerge.RData")

```


```{r Heatmaps before and after merging technical replicates, fig.width=25, fig.height=8}
annot.columns <- c("Subtype", "ASCL1 qPCR", "NEUROD1 qPCR", "POU2F3 qPCR", "YAP1 qPCR", "Cell line origin",
                   "Culture type", "MSbatch", "Data.Acquisiton")
  
draw(Heatmap(t(scale(t(Tables$CP$Expr))), 
                     name="Z-score",
             col=colorRamp2(c(-4, 0, 4), c("blue","white", "red")),
                     cluster_rows = F, top_annotation = create_heatmapannot(Tables$CP$Annot, annot.columns, colorlist), 
             cluster_columns = T, clustering_distance_rows = "euclidean",
             column_split = 4, show_row_names = F, show_heatmap_legend = T, use_raster = T,
             row_title = NULL,height  = unit(0.01, "cm")),
             annotation_legend_side="bottom")

draw(Heatmap(t(scale(t(Tables$CM$Expr))), 
                     name="Z-score",
             col=colorRamp2(c(-4, 0, 4), c("blue","white", "red")),
                     cluster_rows = F, top_annotation = create_heatmapannot(Tables$CM$Annot, annot.columns, colorlist), 
             cluster_columns = T, clustering_distance_rows = "euclidean",
             column_split = 4, show_row_names = F, show_heatmap_legend = T, use_raster = T,
             row_title = NULL,height  = unit(0.01, "cm")),
             annotation_legend_side="bottom")

annot.columns <- c("Subtype", "ASCL1 qPCR", "NEUROD1 qPCR", "POU2F3 qPCR", "YAP1 qPCR", "Cell line origin",
                   "Culture type", "MSbatch")

draw(Heatmap(t(scale(t(Tables$CP$Expr.Med.withinBatch))), 
                     name="Z-score",
             col=colorRamp2(c(-4, 0, 4), c("blue","white", "red")),
                     cluster_rows = F, top_annotation = create_heatmapannot(Tables$CP$Annot.Med.withinBatch, annot.columns, colorlist), 
             cluster_columns = T, clustering_distance_rows = "euclidean",
             column_split = 4, show_row_names = F, show_heatmap_legend = T, use_raster = T,
             row_title = NULL,height  = unit(0.01, "cm")),
             annotation_legend_side="bottom")

draw(Heatmap(t(scale(t(Tables$CM$Expr.Med.withinBatch))), 
                     name="Z-score",
             col=colorRamp2(c(-4, 0, 4), c("blue","white", "red")),
                     cluster_rows = F, top_annotation = create_heatmapannot(Tables$CM$Annot.Med.withinBatch, annot.columns, colorlist), 
             cluster_columns = T, clustering_distance_rows = "euclidean",
             column_split = 4, show_row_names = F, show_heatmap_legend = T, use_raster = T,
             row_title = NULL,height  = unit(0.01, "cm")),
             annotation_legend_side="bottom")

```




```{r PCA plots before and after merging technical replicates, fig.width = 15, fig.height = 10}
annot.columns <- c("Subtype", "Cell line origin",
                   "Culture type", "MSbatch", "Data.Acquisiton")
all(colnames(Tables$CP$Expr) == row.names(Tables$CP$Annot))
all(colnames(Tables$CM$Expr) == row.names(Tables$CM$Annot))

for (i in 1:length(annot.columns)){
  print(ggbiplot(prcomp(t(na.omit(Tables$CP$Expr))),
         circle=F, scale = T, 
         labels=colnames(Tables$CP$Expr), 
         groups = as.factor(Tables$CP$Annot[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CP\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
  print(ggbiplot(prcomp(t(na.omit(Tables$CM$Expr))),
         circle=F, scale = T, 
         labels=colnames(Tables$CM$Expr), 
         groups = as.factor(Tables$CM$Annot[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CM\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
}


annot.columns <- c("Subtype", "Cell line origin",
                   "Culture type", "MSbatch")
all(colnames(Tables$CP$Expr.Med.withinBatch) == row.names(Tables$CP$Annot.Med.withinBatch))
all(colnames(Tables$CM$Expr.Med.withinBatch) == row.names(Tables$CM$Annot.Med.withinBatch))

for (i in 1:length(annot.columns)){
  print(ggbiplot(prcomp(t(na.omit(Tables$CP$Expr.Med.withinBatch))),
         circle=F, scale = T, 
         labels=colnames(Tables$CP$Expr.Med.withinBatch), 
         groups = as.factor(Tables$CP$Annot.Med.withinBatch[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CP (median)\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
  print(ggbiplot(prcomp(t(na.omit(Tables$CM$Expr.Med.withinBatch))),
         circle=F, scale = T, 
         labels=colnames(Tables$CM$Expr.Med.withinBatch), 
         groups = as.factor(Tables$CM$Annot.Med.withinBatch[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CM (median)\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
}


```





```{r Cleaned PCA plots before and after merging technical replicates, fig.width = 15, fig.height = 5}
i= grep("batch", annot.columns)

CP.PCA.before <- ggbiplot(prcomp(t(na.omit(Tables$CP$Expr.Med.withinBatch))),
         circle=F, scale = T, 
         groups = as.factor(Tables$CP$Annot.Med.withinBatch[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CP\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
CM.PCA.before <- ggbiplot(prcomp(t(na.omit(Tables$CM$Expr.Med.withinBatch))),
         circle=F, scale = T, 
         groups = as.factor(Tables$CM$Annot.Med.withinBatch[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CM\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggarrange(CP.PCA.before, CM.PCA.before)

```





# Batch effect correction


```{r Filter for min 1 valid value}
Tables$CP$Expr.Med.withinBatch.F <- filter_missingvalues(Tables$CP$Expr.Med.withinBatch, 1)
Tables$CM$Expr.Med.withinBatch.F <- filter_missingvalues(Tables$CM$Expr.Med.withinBatch, 1)
```


```{r Batch correction,eval=F}
Tables$CP$Expr.Med.withinBatch.F.BatchCorr <- batch_correction_LM(df = Tables$CP$Expr.Med.withinBatch.F, 
                                                                  annot = Tables$CP$Annot.Med.withinBatch[,c("MainID", "MSbatch")])
Tables$CM$Expr.Med.withinBatch.F.BatchCorr <- batch_correction_LM(df = Tables$CM$Expr.Med.withinBatch.F, 
                                                                  annot = Tables$CM$Annot.Med.withinBatch[,c("MainID", "MSbatch")])
save(Tables, file="RData/Tables_afterBatchCorr.RData")
```


```{r }
load("RData/Tables_afterBatchCorr.RData")
```


```{r Heatmaps after batch correction, fig.width=25, fig.height=8}
Tables$CP$Expr.Med.withinBatch.F.BatchCorr <- Tables$CP$Expr.Med.withinBatch.F.BatchCorr[,row.names(Tables$CP$Annot.Med.withinBatch)]
Tables$CM$Expr.Med.withinBatch.F.BatchCorr <- Tables$CM$Expr.Med.withinBatch.F.BatchCorr[,row.names(Tables$CM$Annot.Med.withinBatch)]

annot.columns <- c("Subtype", "ASCL1 qPCR", "NEUROD1 qPCR", "POU2F3 qPCR", "YAP1 qPCR", "Cell line origin",
                   "Culture type", "MSbatch")

draw(Heatmap(t(scale(t(Tables$CP$Expr.Med.withinBatch.F.BatchCorr))), 
                     name="Z-score",
             col=colorRamp2(c(-4, 0, 4), c("blue","white", "red")),
                     cluster_rows = F, 
             top_annotation = create_heatmapannot(Tables$CP$Annot.Med.withinBatch, annot.columns, colorlist), 
             cluster_columns = T, clustering_distance_columns = "pearson",
             #column_split = 4, 
             show_row_names = F, show_heatmap_legend = T, 
             row_title = NULL,height  = unit(0.01, "cm")),
             annotation_legend_side="bottom")

draw(Heatmap(t(scale(t(Tables$CM$Expr.Med.withinBatch.F.BatchCorr))), 
                     name="Z-score",
             col=colorRamp2(c(-4, 0, 4), c("blue","white", "red")),
                     cluster_rows = F, top_annotation = create_heatmapannot(Tables$CM$Annot.Med.withinBatch, annot.columns, colorlist), 
             cluster_columns = T, clustering_distance_columns = "pearson",
             #column_split = 4, 
             show_row_names = F, show_heatmap_legend = T, 
             row_title = NULL,height  = unit(0.01, "cm")),
             annotation_legend_side="bottom")

```






```{r PCA plots after batch correction, fig.width = 15, fig.height = 5}
annot.columns <- c("Subtype", "Cell line origin",
                   "Culture type", "MSbatch")
all(colnames(Tables$CP$Expr.Med.withinBatch.F.BatchCorr) == row.names(Tables$CP$Annot.Med.withinBatch))
all(colnames(Tables$CM$Expr.Med.withinBatch.F.BatchCorr) == row.names(Tables$CM$Annot.Med.withinBatch))

for (i in 1:length(annot.columns)){
  print(ggbiplot(prcomp(t(na.omit(Tables$CP$Expr.Med.withinBatch.F.BatchCorr))),
         circle=F, scale = T, 
         labels=colnames(Tables$CP$Expr.Med.withinBatch.F.BatchCorr), 
         groups = as.factor(Tables$CP$Annot.Med.withinBatch[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CP (median)\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
  print(ggbiplot(prcomp(t(na.omit(Tables$CM$Expr.Med.withinBatch.F.BatchCorr))),
         circle=F, scale = T, 
         labels=colnames(Tables$CM$Expr.Med.withinBatch.F.BatchCorr), 
         groups = as.factor(Tables$CM$Annot.Med.withinBatch[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CM (median)\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
}


```




```{r Cleaned PCA plots after batch correction, fig.width = 15, fig.height = 5}
i= grep("batch", annot.columns)

CP.PCA.after <- ggbiplot(prcomp(t(na.omit(Tables$CP$Expr.Med.withinBatch.F.BatchCorr))),
         circle=F, scale = T, 
         #labels=colnames(Tables$CP$Expr), 
         groups = as.factor(Tables$CP$Annot.Med.withinBatch[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CP\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
CM.PCA.after <- ggbiplot(prcomp(t(na.omit(Tables$CM$Expr.Med.withinBatch.F.BatchCorr))),
         circle=F, scale = T, 
         #labels=colnames(Tables$CM$Expr.Med.withinBatch), 
         groups = as.factor(Tables$CM$Annot.Med.withinBatch[,annot.columns[i]]),
         ellipse = T,
         var.axes	=F) + 
  ggtitle(paste0("CM\n  Categorized by: ", annot.columns[i]))+
  theme_bw()+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

ggarrange(CP.PCA.after, CM.PCA.after)

```




```{r }
Fig_QC_PCA_PVCA_HC <- Tables
save(Fig_QC_PCA_PVCA_HC, file="RData/Fig_QC_PCA_PVCA_HC.RData")
```


# Merging replicates from different batch



```{r Mean of replicates from different batches, eval=F}

for (i in 1:2){
  Tables[[i]]$Annot.AvrRepl <- Tables[[i]]$Annot.Med.withinBatch
  Tables[[i]]$Annot.AvrRepl$MainID <- unlist(lapply(Tables[[i]]$Annot.AvrRepl$Replicate, function(x){
    strsplit(x, split="_")[[1]][1]
  }))
  Tables[[i]]$Annot.AvrRepl$Replicate <- NULL
  Tables[[i]]$Annot.AvrRepl$MSbatch <- NULL
  Tables[[i]]$Annot.AvrRepl <- unique(Tables[[i]]$Annot.AvrRepl)
  Tables[[i]]$Expr.Med.withinBatch.F.BatchCorr.Avr <- mean_of_repeated_measurements(Tables[[i]]$Expr.Med.withinBatch.F.BatchCorr,
                                                                                      Tables[[i]]$Annot.AvrRepl$MainID,
                                                                                    "_" )
}

save(Tables, file="RData/Tables_afterAveragingReplicates_fromDiffBatch.RData")

```



```{r }
load("RData/Tables_afterAveragingReplicates_fromDiffBatch.RData")
```


# Export tables



```{r Remove non-SCLC samples and export}

SCLC.samples <- Tables$CP$Annot.AvrRepl[!is.na(Tables$CP$Annot.AvrRepl$Subtype),"MainID"]
cell.line.IDs <- Tables$CP$Annot.AvrRepl[!is.na(Tables$CP$Annot.AvrRepl$Subtype),"Sample"]
CP.expr.final <- filter_missingvalues(Tables$CP$Expr.Med.withinBatch.F.BatchCorr.Avr[,SCLC.samples], 80)
colnames(CP.expr.final) <- cell.line.IDs
CM.expr.final <- filter_missingvalues(Tables$CM$Expr.Med.withinBatch.F.BatchCorr.Avr[,SCLC.samples], 80)
colnames(CM.expr.final) <- cell.line.IDs

#export_with_rowname(Tables$CP$Expr.Med.withinBatch.F.BatchCorr.Avr[,SCLC.samples], "Files/CP_expression_full",T)
#export_with_rowname(Tables$CM$Expr.Med.withinBatch.F.BatchCorr.Avr[,SCLC.samples], "Files/CM_expression_full",T)
#export_with_rowname(CP.expr.final, "Files/CP_expression_filtered",T)
#export_with_rowname(CM.expr.final, "Files/CM_expression_filtered",T)
#export_with_rowname(Tables$CP$Info, "Files/CP_protein_info_full",T)
#export_with_rowname(Tables$CM$Info, "Files/CM_protein_info_full",T)
```


