---
title: "Secreted, surface and plasma proteins"
author: Beata Szeitz
output:
  html_notebook:
    toc: yes
---


# Load packages, functions and files


```{r }
# R vs.4.2.0
source("Load_packages.R")
source("Utility_functions.R")
source("Color_list.R")
```

# Secreted proteins

## Load Human Protein Atlas, MetazSecKB and SPRomeDB data


MetazSecKB: load curated, highly likely, likely and weakly likely secreted protein list separately (see file names below)


```{r }
curated.Secreted <- read.delim("Files/Localization/MetazSecKB/secreted (curated).txt", header = F)
highlyLikely.Secreted <- read.delim("Files/Localization/MetazSecKB/highly likely secreted.txt", header = F)
Likely.Secreted <- read.delim("Files/Localization/MetazSecKB/likely secreted.txt", header = F)
weaklyLikely.Secreted <- read.delim("Files/Localization/MetazSecKB/weakly likely secreted.txt", header = F)

```


SPRomeDB: load the secreted protein list (see file name below)


```{r }
SPRomeDB <- read.csv("Files/Localization/secreted_proteins_SPRomeDB.csv")
SPRomeDB.allProteinIDs <- SPRomeDB$UniProt_ID
SPRomeDB.allProteinIDs <- unique(unlist(lapply(SPRomeDB.allProteinIDs, strsplit, split=";")))
SPRomeDB.allProteinIDs <- SPRomeDB.allProteinIDs[SPRomeDB.allProteinIDs!="NA"]
```

HPA: load the secreted protein list (see file name below)


```{r }
HPA.secr <- read.delim("Files/Localization/protein_class_PredictedSecr_downloaded-on-2021-04-11.tsv")
#length(unique(HPA.secr$Gene))
```




## Clean the tables


HPA sometimes mentions multiple protein accessions for the same gene: these were put into separate rows.

```{r }
HPA.secr.proteins <- HPA.secr[,c("Gene", "Uniprot")]

for (i in 1:nrow(HPA.secr.proteins)){
  if (grepl(",", HPA.secr.proteins$Uniprot[i], fixed=T)){
    #cutted <- strsplit(HPA.secr.proteins$Uniprot[i], split="")[[1]]
    #print(grep(",", cutted))
    proteins <- strsplit(HPA.secr.proteins$Uniprot[i], split=", ", fixed = T)[[1]]
    HPA.secr.proteins$Uniprot[i] <- proteins[1]
    # rbind(df, setNames(de, names(df)))
    
    newrow <- data.frame(HPA.secr.proteins$Gene[i], proteins[2])
    
    HPA.secr.proteins <- rbind(HPA.secr.proteins, setNames(newrow, names(HPA.secr.proteins)))
  }
}
```


Only SPromeDB entails isoforms; thus, the isoform part of the accession was removed (-1, -2 etc) to only keep the canonical accessions.

```{r }
SPRomeDB.proteins <- SPRomeDB[,c("UniProt_ID")]
SPRomeDB.proteins <- unique(unlist(lapply(SPRomeDB.proteins, function(x){strsplit(x,";", fixed=T)[[1]][1]})))
SPRomeDB.proteins.can <- unique(unlist(lapply(SPRomeDB.proteins, function(x){strsplit(x, "-", fixed=T)[[1]][1]})))
grep("-", SPRomeDB.proteins.can, fixed=T)
```

As MetazSecKB also categorizes the proteins based on strength of evidence, I kept this information in the table. However, weakly likely secreted proteins were almost never Tier 1 or 2.


```{r }

MetazSecKB.secr.proteins <- c(curated.Secreted[,1], highlyLikely.Secreted[,1], Likely.Secreted[,1], weaklyLikely.Secreted[,1])

MetazSecKB.secr.proteins.Tier <- c(rep("curated",length(curated.Secreted[,1])),
                                   rep("highlyLikely",length(highlyLikely.Secreted[,1])),
                                   rep("Likely",length(Likely.Secreted[,1])),
                                   rep("weaklyLikely",length(weaklyLikely.Secreted[,1])))
names(MetazSecKB.secr.proteins.Tier) <- MetazSecKB.secr.proteins


```

In summary, 31224 proteins will be present in the summarized secreted protein table based on the 3 databases.

```{r }
secreted.proteins.can <- unique(c(HPA.secr.proteins$Uniprot, MetazSecKB.secr.proteins, SPRomeDB.proteins.can))
secreted.proteins.can <- secreted.proteins.can[secreted.proteins.can!=""]
secreted.proteins.can <- secreted.proteins.can[secreted.proteins.can!="NA"]

length(secreted.proteins.can)
```
## Creating and exporting the summarized secreted protein table


```{r ,eval=F}
All.Secreted.proteins <- as.data.frame(matrix(nrow=length(secreted.proteins.can), ncol=4))
row.names(All.Secreted.proteins) <-secreted.proteins.can
colnames(All.Secreted.proteins) <- c("HPA", "MetazSecKB","MetazSecKB_Category", "SPRomeDB")

i=1
for (i in 1:nrow(All.Secreted.proteins)){
  All.Secreted.proteins[i,1] <- ifelse(row.names(All.Secreted.proteins)[i] %in% HPA.secr.proteins$Uniprot, "*", "")
  All.Secreted.proteins[i,2] <- ifelse(row.names(All.Secreted.proteins)[i] %in% MetazSecKB.secr.proteins, "*", "")
  All.Secreted.proteins[i,4] <- ifelse(row.names(All.Secreted.proteins)[i] %in% SPRomeDB.proteins.can, "*", "")
  All.Secreted.proteins[i,3] <- MetazSecKB.secr.proteins.Tier[row.names(All.Secreted.proteins)[i]]
}

All.Secreted.proteins$Present <- paste(All.Secreted.proteins$HPA, All.Secreted.proteins$MetazSecKB, All.Secreted.proteins$SPRomeDB, sep="")

for (i in 1:nrow(All.Secreted.proteins)){
  if (All.Secreted.proteins$Present[i] == "***"){
    All.Secreted.proteins$Tier[i] <- "1"
  } else if (All.Secreted.proteins$Present[i] == "**"){
    All.Secreted.proteins$Tier[i] <- "2"
  } else if (All.Secreted.proteins$Present[i] == "*"){
    All.Secreted.proteins$Tier[i] <- "3"
  }
}

All.Secreted.proteins$Protein <- row.names(All.Secreted.proteins)

All.Secreted.proteins <- All.Secreted.proteins[,c("Protein", "Tier", "HPA", "SPRomeDB", "MetazSecKB", "MetazSecKB_Category")]
All.Secreted.proteins <- All.Secreted.proteins[order(All.Secreted.proteins$Tier),]

#Export this protein secretion info table (Secreted_Protein_Table_HPA_MetazSecKB_SPRomeDB.txt) for future use
export_with_rowname(All.Secreted.proteins, "Files/Secreted_Protein_Table_HPA_MetazSecKB_SPRomeDB", F)
export_with_rowname(Only.secreted, "Files/Tier1_and_2_secreted", F)

```


```{r }

All.Secreted.proteins <- read_in_with_rowname("Files/Secreted_Protein_Table_HPA_MetazSecKB_SPRomeDB",F)

Protein.to.gene <- read_in_with_rowname("Files/Protein_to_Gene",F)

Protein.to.gene.Secr <- merge(Protein.to.gene, All.Secreted.proteins, by="Protein", all.x=T)
Protein.to.gene.Secr[is.na(Protein.to.gene.Secr)] <- ""
colnames(Protein.to.gene.Secr) <- c("Protein","Gene","Secr.Tier" ,"Secr.HPA","SPRomeDB","MetazSecKB" ,"MetazSecKB_Category")


```



## Visualize the Tier 1-4 proteins



```{r }
CP.expr <- read_in_with_rowname("Files/CP_expression_full",F)
CM.expr <- read_in_with_rowname("Files/CM_expression_full",F)

SD.CP <- apply(CP.expr, 1, sd, na.rm=TRUE)
SD.CM <- apply(CM.expr, 1, sd, na.rm=TRUE)

Mean.CP <- apply(CP.expr, 1, mean, na.rm=TRUE)
Mean.CM <- apply(CM.expr, 1, mean, na.rm=TRUE)

VVs.CP <- apply(CP.expr, 1, function(x){sum(!is.na(x))})
VVs.CM <- apply(CM.expr, 1, function(x){sum(!is.na(x))})

secr <- read_in_with_rowname("Files/Tier1_and_2_secreted",F)[,1]

```



```{r }
SD.dataframe <- data.frame(Protein = unique( c(row.names(CP.expr), row.names(CM.expr))))

for (i in 1:nrow(SD.dataframe)){
  SD.dataframe$CP.SD[i] <- SD.CP[SD.dataframe$Protein[i]]
  SD.dataframe$CM.SD[i] <- SD.CM[SD.dataframe$Protein[i]]
  
  SD.dataframe$CP.Mean[i] <- Mean.CP[SD.dataframe$Protein[i]]
  SD.dataframe$CM.Mean[i] <- Mean.CM[SD.dataframe$Protein[i]]
  
  if (SD.dataframe$Protein[i] %in% All.Secreted.proteins$Protein){
    secrInfo <- All.Secreted.proteins[All.Secreted.proteins$Protein == SD.dataframe$Protein[i],"Tier"]
  } else {
    secrInfo <- "4"
  }
  
  SD.dataframe$Secretion_info[i] <- secrInfo
  
  
  SD.dataframe$CP.VVs[i] <- VVs.CP[SD.dataframe$Protein[i]]
  SD.dataframe$CM.VVs[i] <- VVs.CM[SD.dataframe$Protein[i]]
}

```



```{r , fig.width=10, fig.height=5}

g1 <- ggplot(SD.dataframe, aes(x=Secretion_info, y=CP.VVs)) +
  geom_boxplot()+ theme_bw()+scale_fill_brewer(palette="Set1")+
  xlab("Secretion Tier") + ylab("#Valid values across samples") + ggtitle("CP")

g2 <- ggplot(SD.dataframe, aes(x=Secretion_info, y=CM.VVs)) +
  geom_boxplot()+ theme_bw()+scale_fill_brewer(palette="Set1")+
  xlab("Secretion Tier") + ylab("#Valid values across samples") + ggtitle("CM")

ggarrange(g1, g2)

```



```{r , fig.width=10, fig.height=6}


p <- ggplot(SD.dataframe, aes(x = CP.Mean, y = CP.SD)) +
    geom_point(alpha=0.5,aes(color = Secretion_info))+ theme_classic() + 
  theme(legend.position = "bottom") + ggtitle("CP") + 
  xlab("Protein mean intensity") + ylab("Protein standard deviation")+
  scale_colour_manual( values=c("1" = "red", "2" = "blue", "3" = "lightgreen", "4" = "grey"))+
  xlim(c(9, 33)) + ylim(c(0,5.5))
p1 <- ggExtra::ggMarginal(p, type = "density", groupFill  = TRUE)


p <- ggplot(SD.dataframe, aes(x = CM.Mean, y = CM.SD)) +
    geom_point(alpha=0.5,aes(color = Secretion_info))+ theme_classic() + 
  theme(legend.position = "bottom")  + ggtitle("CM") + 
  xlab("Protein mean intensity") + ylab("Protein standard deviation")+
  scale_colour_manual( values=c("1" = "red", "2" = "blue", "3" = "lightgreen", "4" = "grey"))+
  xlim(c(9, 33)) + ylim(c(0,5.5))
p2 <- ggExtra::ggMarginal(p, type = "density", groupFill  = TRUE)

ggarrange(p1,p2, ncol=2)

```

```{r Export RData for figure}
#Fig_secreted <- SD.dataframe
#save(Fig_secreted, file="RData/Fig_secreted.RData")
```


# Cell-surface proteins

Tier 1: present in both DBs; Tier 2: only present in one DB

```{r }

Hu <- read.xlsx("Files/Localization/Cancer_Surfaceome_Atlas_28June2022.xlsx",sheet=1)
Bausch <- read.xlsx("Files/Localization/Surfaceome_Bausch-Fluck_28June2022.xlsx",sheet=1)

head(Bausch)
unique(Bausch$X5)

Hu.surface.genes <- unique(Hu[-c(1:3),2])
Bausch.surface.genes <- unique(Bausch[Bausch$X5 =="surface",4])

length(intersect(Hu.surface.genes, Bausch.surface.genes))

Protein.to.gene.Secr$Surf.Tier <- 3
Protein.to.gene.Secr$Surf.Hu <- ""
Protein.to.gene.Secr$Surf.BauschFluck <- ""

for (i in 1:nrow(Protein.to.gene.Secr)){
  Protein.to.gene.Secr$Surf.Hu[i] <- ifelse(Protein.to.gene.Secr$Gene[i] %in% Hu.surface.genes, "*","")
  Protein.to.gene.Secr$Surf.BauschFluck[i] <- ifelse(Protein.to.gene.Secr$Gene[i] %in% Bausch.surface.genes, "*","")
  Protein.to.gene.Secr$Surf.Tier[i] <- ifelse(Protein.to.gene.Secr$Surf.Hu[i] =="*" & Protein.to.gene.Secr$Surf.BauschFluck[i] =="*",
                                              1, Protein.to.gene.Secr$Surf.Tier[i])
  Protein.to.gene.Secr$Surf.Tier[i] <- ifelse(Protein.to.gene.Secr$Surf.Hu[i] !="*" & Protein.to.gene.Secr$Surf.BauschFluck[i] =="*",
                                              2, Protein.to.gene.Secr$Surf.Tier[i])
  Protein.to.gene.Secr$Surf.Tier[i] <- ifelse(Protein.to.gene.Secr$Surf.Hu[i] =="*" & Protein.to.gene.Secr$Surf.BauschFluck[i] !="*",
                                              2, Protein.to.gene.Secr$Surf.Tier[i])
}


```

# Plasma proteins

Human blood plasma proteins detected by MS, PEA or immunoassay

```{r }
#Blood.proteins <- read.xlsx("Files/Localization/PeptideAtlas_Human_Plasma_2021-07_vs23July2022.xlsx",sheet=1)
#colnames(Blood.proteins)[1] <- "Protein"

Blood.proteins.immuno <- read.xlsx("Files/Localization/HPA_blood_proteins_PEA_MS_immunoassay_vs23July2022.xlsx",sheet=3)
Blood.proteins.immuno <- Blood.proteins.immuno[,-4]
Blood.proteins.immuno <- Blood.proteins.immuno[!is.na(Blood.proteins.immuno$Gene),]

Blood.proteins.PEA <- read.xlsx("Files/Localization/HPA_blood_proteins_PEA_MS_immunoassay_vs23July2022.xlsx",sheet=1)
Blood.proteins.MS <- read.xlsx("Files/Localization/HPA_blood_proteins_PEA_MS_immunoassay_vs23July2022.xlsx",sheet=2)

Blood.proteins.All <- data.frame(Gene = unique(c(Blood.proteins.immuno$Gene, Blood.proteins.PEA$Gene, Blood.proteins.MS$Gene)),
                                 Detected.in.blood.by = NA)

for (i in 1:nrow(Blood.proteins.All)){
  methods <- vector()
  if (Blood.proteins.All$Gene[i] %in% Blood.proteins.immuno$Gene){
    methods <- c(methods, "Immunoassay")
  }
  
  if (Blood.proteins.All$Gene[i] %in% Blood.proteins.MS$Gene){
    methods <- c(methods, "MS")
  }
  
  if (Blood.proteins.All$Gene[i] %in% Blood.proteins.PEA$Gene){
    methods <- c(methods, "PEA")
  }
  
  
  Blood.proteins.All$Detected.in.blood.by[i] <- paste(methods, collapse = ", ")
  
}


Actively.secreted <- read.delim("Files/Localization/HPA_secreted_to_blood.tsv")

#HPA.conc.table <- read.xlsx("Files/Localization/Proteins_detected_by_blood_HPA.xlsx",sheet=2)


Plasma.proteins.export <- unique(merge(Protein.to.gene, 
                                          Blood.proteins.All[,c("Gene", "Detected.in.blood.by")], by="Gene"))

```

```{r }
Protein.to.gene.Secr.Surf.Plasma <- merge(Protein.to.gene.Secr, 
                                          Blood.proteins.All[,c("Gene", "Detected.in.blood.by")], by="Gene", all.x=T)


for (i in 1:nrow(Protein.to.gene.Secr.Surf.Plasma)){
  #if (Protein.to.gene.Secr.Surf.Plasma$Gene[i] %in% HPA.conc.table$Gene){
  #  Protein.to.gene.Secr.Surf.Plasma$Est.conc[i] <- HPA.conc.table[HPA.conc.table$Gene==Protein.to.gene.Secr.Surf.Plasma$Gene[i],"Concentration"]
  #} else {
  #  Protein.to.gene.Secr.Surf.Plasma$Est.conc[i] <- ""
  #}
  
  if (Protein.to.gene.Secr.Surf.Plasma$Protein[i] %in% Actively.secreted$Uniprot){
    Protein.to.gene.Secr.Surf.Plasma$Actively.secr.in.blood[i] <- "*"
  } else {
    Protein.to.gene.Secr.Surf.Plasma$Actively.secr.in.blood[i] <- ""
  }
  
}


Protein.to.gene.Secr.Surf.Plasma[is.na(Protein.to.gene.Secr.Surf.Plasma)] <- ""
Protein.to.gene.Secr.Surf.Plasma$Secr.Tier <- ifelse(Protein.to.gene.Secr.Surf.Plasma$Secr.Tier =="",4,
                                                     Protein.to.gene.Secr.Surf.Plasma$Secr.Tier)

```



## Summary on the number of detected plasma proteins


```{r }

CP.expr <- read_in_with_rowname("Files/CP_expression_full",F)
nrow(CP.expr[row.names(CP.expr) %in% Actively.secreted$Uniprot,])
nrow(CP.expr[row.names(CP.expr) %in% Plasma.proteins.export$Protein,])

CM.expr <- read_in_with_rowname("Files/CM_expression_full",F)
nrow(CM.expr[row.names(CM.expr) %in% Actively.secreted$Uniprot,])
nrow(CM.expr[row.names(CM.expr) %in% Plasma.proteins.export$Protein,])


CP.expr.imp <- read_in_with_rowname("Files/CP_expression_filtered_imputed",F)
nrow(CP.expr.imp[row.names(CP.expr.imp) %in% Actively.secreted$Uniprot,])
nrow(CP.expr.imp[row.names(CP.expr.imp) %in% Actively.secreted$Uniprot,]) - nrow(CP.expr[row.names(CP.expr) %in% Actively.secreted$Uniprot,])

nrow(CP.expr.imp[row.names(CP.expr.imp) %in% Plasma.proteins.export$Protein,])
nrow(CP.expr.imp[row.names(CP.expr.imp) %in% Plasma.proteins.export$Protein,]) -  nrow(CP.expr[row.names(CP.expr) %in% Plasma.proteins.export$Protein,])

CM.expr.imp <- read_in_with_rowname("Files/CM_expression_filtered_imputed",F)
nrow(CM.expr.imp[row.names(CM.expr.imp) %in% Actively.secreted$Uniprot,])
nrow(CM.expr.imp[row.names(CM.expr.imp) %in% Actively.secreted$Uniprot,]) - nrow(CM.expr[row.names(CM.expr) %in% Actively.secreted$Uniprot,])
nrow(CM.expr.imp[row.names(CM.expr.imp) %in% Plasma.proteins.export$Protein,])
nrow(CM.expr.imp[row.names(CM.expr.imp) %in% Plasma.proteins.export$Protein,]) - nrow(CM.expr[row.names(CM.expr) %in% Plasma.proteins.export$Protein,])





```


```{r , fig.width=5, fig.height=3}
Blood.proteins.rankplot <- Plasma.proteins.export
Blood.proteins.rankplot$Detected <- "None"

for (i in 1:nrow(Blood.proteins.rankplot)){
  if (Blood.proteins.rankplot$Protein[i] %in% row.names(CP.expr) & 
      Blood.proteins.rankplot$Protein[i] %in% row.names(CM.expr)){
    Blood.proteins.rankplot$Detected[i] <- "CP&CM"
  } else if (Blood.proteins.rankplot$Protein[i] %in% row.names(CP.expr)){
    Blood.proteins.rankplot$Detected[i] <- "CP"
  } else if (Blood.proteins.rankplot$Protein[i] %in% row.names(CM.expr)){
    Blood.proteins.rankplot$Detected[i] <- "CM"
  } 
}


#Blood.proteins.rankplot <- Blood.proteins.rankplot[order(Blood.proteins.rankplot$norm_PSMs_per_100K, decreasing = T),]
#Blood.proteins.rankplot$Rank <- seq(1,nrow(Blood.proteins.rankplot),1)
#Blood.proteins.rankplot$log10_norm_PSMs_per_100K <- log10(Blood.proteins.rankplot$norm_PSMs_per_100K)

#ggplot(Blood.proteins.rankplot[Blood.proteins.rankplot$Detected !="CP&CM",], aes(x=Rank,y=log10_norm_PSMs_per_100K, color=Detected))+
#  geom_point(size=1, alpha=0.8)+
#  scale_color_manual(values=c("blue", "darkgrey"))+ 
##  theme_bw()+geom_line()


#ggplot(Blood.proteins.rankplot, aes(x=log10_norm_PSMs_per_100K, fill=Detected))+
#  geom_density(alpha=0.5)+
#  scale_fill_manual(values=c("lightblue", "beige","white"))+ 
#  theme_classic()+xlab("log10 (spectra count per 100K)")+ggtitle("Distribution of Human Plasma Proteins")

```



# Druggable proteins


```{r }

enzymes <- unique(read.table("Files/Druggable/protein_class_FDA (1)_Enzymes.tsv", header = TRUE, fill=TRUE)[,1])
transporters <- unique(read.table("Files/Druggable/protein_class_FDA (2)_Transporters.tsv", header = TRUE, fill=TRUE)[,1])
G.protein.coupled.receptors <- unique(read.table("Files/Druggable/protein_class_FDA (3)_G-protein coupled receptors.tsv", header = TRUE, fill=TRUE)[,1])
CD.markers <- unique(read.table("Files/Druggable/protein_class_FDA (4)_CD markers.tsv", header = TRUE, fill=TRUE)[,1])
Voltage.gated.ion.channels <- unique(read.table("Files/Druggable/protein_class_FDA (5)_Voltage-gated ion channels.tsv", header = TRUE, fill=TRUE)[,1])
Nuclear.receptors <- unique(read.table("Files/Druggable/protein_class_FDA (6)_Nuclear receptors.tsv", header = TRUE, fill=TRUE)[,1])

```


```{r }

Protein.to.gene.Secr.Surf.Plasma.Druggable <- Protein.to.gene.Secr.Surf.Plasma

Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable.Enzyme <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Gene %in% enzymes, "*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable.Transporter <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Gene %in% transporters, "*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable.G.protein.coupled.receptor <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Gene %in% G.protein.coupled.receptors, "*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable.CD.marker <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Gene %in% CD.markers, "*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable.Voltage.gated.ion.channel <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Gene %in% Voltage.gated.ion.channels, "*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable.Nuclear.receptor <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Gene %in% Nuclear.receptors, "*","")


```


# Export all protein annotations in one file


```{r }

Protein.to.gene.Secr.Surf.Plasma.Druggable$Accession <- Protein.to.gene.Secr.Surf.Plasma.Druggable$Protein
Protein.to.gene.Secr.Surf.Plasma.Druggable$Secreted <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Secr.Tier < 3, "*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$Surface <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Surf.Tier ==1, "*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$Plasma.detect <- ifelse(nchar(Protein.to.gene.Secr.Surf.Plasma.Druggable$Detected.in.blood.by)>0, "*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$Blood.secr <- Protein.to.gene.Secr.Surf.Plasma.Druggable$Actively.secr.in.blood

columns <- grep("Drugg",colnames(Protein.to.gene.Secr.Surf.Plasma.Druggable))
names(columns) <- gsub("Druggable.","",colnames(Protein.to.gene.Secr.Surf.Plasma.Druggable)[columns], fixed=T)
names(columns) <- gsub("."," ",names(columns) , fixed=T)

Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable <- ""

 #i=175
for (i in 1:nrow(Protein.to.gene.Secr.Surf.Plasma.Druggable)){
  short.df <- Protein.to.gene.Secr.Surf.Plasma.Druggable[i,columns]
  for (j in 1:ncol(short.df)){
    short.df[1,j] <- ifelse(short.df[1,j]=="*", names(columns)[j],NA)
  }
  short.df <- short.df[!is.na(short.df)]
  Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable[i] <- paste(short.df, collapse = ", ")
  
}


Protein.to.gene.Secr.Surf.Plasma.Druggable$CP <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Protein %in% row.names(CP.expr),"*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$CP.imp <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Protein %in% row.names(CP.expr.imp),"*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$CM <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Protein %in% row.names(CM.expr),"*","")
Protein.to.gene.Secr.Surf.Plasma.Druggable$CM.imp <- ifelse(Protein.to.gene.Secr.Surf.Plasma.Druggable$Protein %in% row.names(CM.expr.imp),"*","")

export_with_rowname(Protein.to.gene.Secr.Surf.Plasma.Druggable, "Files/Secreted_surface_plasma_druggable_info",F)

```



# Summary of the numbers


```{r }
nrow(Protein.to.gene.Secr.Surf.Plasma.Druggable[Protein.to.gene.Secr.Surf.Plasma.Druggable$Secreted =="*",])
nrow(Protein.to.gene.Secr.Surf.Plasma.Druggable[Protein.to.gene.Secr.Surf.Plasma.Druggable$Surface =="*",])
nrow(Protein.to.gene.Secr.Surf.Plasma.Druggable[Protein.to.gene.Secr.Surf.Plasma.Druggable$Plasma.detect =="*",])
nrow(Protein.to.gene.Secr.Surf.Plasma.Druggable[Protein.to.gene.Secr.Surf.Plasma.Druggable$Blood.secr =="*",])
nrow(Protein.to.gene.Secr.Surf.Plasma.Druggable[Protein.to.gene.Secr.Surf.Plasma.Druggable$Druggable !="",])

```

```{r }
Protein.to.gene.Secr.Surf.Plasma.Druggable.CP <- Protein.to.gene.Secr.Surf.Plasma.Druggable[Protein.to.gene.Secr.Surf.Plasma.Druggable$CP=="*",]
Protein.to.gene.Secr.Surf.Plasma.Druggable.CM <- Protein.to.gene.Secr.Surf.Plasma.Druggable[Protein.to.gene.Secr.Surf.Plasma.Druggable$CM=="*",]

CP.summary <- list(Secreted = Protein.to.gene.Secr.Surf.Plasma.Druggable.CP[Protein.to.gene.Secr.Surf.Plasma.Druggable.CP$Secreted=="*","Gene"],
                   Surface = Protein.to.gene.Secr.Surf.Plasma.Druggable.CP[Protein.to.gene.Secr.Surf.Plasma.Druggable.CP$Surface=="*","Gene"],
                   Plasma= unique(c(Protein.to.gene.Secr.Surf.Plasma.Druggable.CP[Protein.to.gene.Secr.Surf.Plasma.Druggable.CP$Plasma.detect=="*","Gene"],
                                    Protein.to.gene.Secr.Surf.Plasma.Druggable.CP[Protein.to.gene.Secr.Surf.Plasma.Druggable.CP$Blood.secr=="*","Gene"])),
                   Druggable = Protein.to.gene.Secr.Surf.Plasma.Druggable.CP[Protein.to.gene.Secr.Surf.Plasma.Druggable.CP$Druggable!="","Gene"])

nrow(Protein.to.gene.Secr.Surf.Plasma.Druggable.CP[!Protein.to.gene.Secr.Surf.Plasma.Druggable.CP$Gene %in%
                                                     unlist(CP.summary),])


CM.summary <- list(Secreted = Protein.to.gene.Secr.Surf.Plasma.Druggable.CM[Protein.to.gene.Secr.Surf.Plasma.Druggable.CM$Secreted=="*","Gene"],
                   Surface = Protein.to.gene.Secr.Surf.Plasma.Druggable.CM[Protein.to.gene.Secr.Surf.Plasma.Druggable.CM$Surface=="*","Gene"],
                   Plasma= unique(c(Protein.to.gene.Secr.Surf.Plasma.Druggable.CM[Protein.to.gene.Secr.Surf.Plasma.Druggable.CM$Plasma.detect=="*","Gene"],
                                    Protein.to.gene.Secr.Surf.Plasma.Druggable.CM[Protein.to.gene.Secr.Surf.Plasma.Druggable.CM$Blood.secr=="*","Gene"])),
                   Druggable = Protein.to.gene.Secr.Surf.Plasma.Druggable.CM[Protein.to.gene.Secr.Surf.Plasma.Druggable.CM$Druggable!="","Gene"])

nrow(Protein.to.gene.Secr.Surf.Plasma.Druggable.CM[!Protein.to.gene.Secr.Surf.Plasma.Druggable.CM$Gene %in%
                                                     unlist(CM.summary),])

```



```{r , fig.width=3, fig.height=3}

ggvenn(
  CP.summary, 
    fill_color = c("#fff9eb", "#fff3d6", "#ffe1b4", "#eec892"),
  stroke_size = 1, set_name_size = 3,show_percentage = F,stroke_color = "grey"
  )


ggvenn(
  CM.summary, 
    fill_color = c("#e0f8f8", "#c2f1f1","#a3ebeb", "#85e4e4"),
  stroke_size = 1, set_name_size = 3,show_percentage = F,stroke_color = "grey"
  )

```




