---
title: "Selection of secreted proteins"
author: Beata Szeitz
output:
  html_notebook:
    toc: yes
---



# Load functions and files


```{r Load packages}
.packages = c("readxl","openxlsx","ggplot2","ggpubr")
lapply(.packages, require, character.only=TRUE)
source("Utility_functions.R")
source("Color_list.R")
```


# Load Human Protein Atlas, MetazSecKB and SPRomeDB data


MetazSecKB: load curated, highly likely, likely and weakly likely secreted protein list separately (see file names below)


```{r }
curated.Secreted <- read.delim("Files/Localization/MetazSecKB/secreted (curated).txt", header = F)
highlyLikely.Secreted <- read.delim("Files/Localization/MetazSecKB/highly likely secreted.txt", header = F)
Likely.Secreted <- read.delim("Files/Localization/MetazSecKB/likely secreted.txt", header = F)
weaklyLikely.Secreted <- read.delim("Files/Localization/MetazSecKB/weakly likely secreted.txt", header = F)

```


SPRomeDB: load the secreted protein list (see file name below)


```{r }
SPRomeDB <- read.csv("Files/Localization/secreted_proteins_SPRomeDB.csv")
SPRomeDB.allProteinIDs <- SPRomeDB$UniProt_ID
SPRomeDB.allProteinIDs <- unique(unlist(lapply(SPRomeDB.allProteinIDs, strsplit, split=";")))
SPRomeDB.allProteinIDs <- SPRomeDB.allProteinIDs[SPRomeDB.allProteinIDs!="NA"]
```

HPA: load the secreted protein list (see file name below)


```{r }
HPA.secr <- read.delim("Files/Localization/protein_class_PredictedSecr_downloaded-on-2021-04-11.tsv")
#length(unique(HPA.secr$Gene))
```




# Clean the tables


MetazSecKB indicates whether only a protein fragment should be secreted - I deleted these instances (you can see the number for these below: All = before deletion, Fragment = the number of deleted instances)


```{r }
curated.Secreted$Fragment <- ifelse(grepl("(Fragment)",curated.Secreted$V4), 1,0)
highlyLikely.Secreted$Fragment <- ifelse(grepl("(Fragment)",highlyLikely.Secreted$V4), 1,0)
Likely.Secreted$Fragment <- ifelse(grepl("(Fragment)",Likely.Secreted$V4), 1,0)
weaklyLikely.Secreted$Fragment <- ifelse(grepl("(Fragment)",weaklyLikely.Secreted$V4), 1,0)

curated.Secreted.full <- curated.Secreted[curated.Secreted$Fragment==0,1]
highlyLikely.Secreted.full <- highlyLikely.Secreted[highlyLikely.Secreted$Fragment==0,1]
Likely.Secreted.full <- Likely.Secreted[Likely.Secreted$Fragment==0,1]
weaklyLikely.Secreted.full <- weaklyLikely.Secreted[weaklyLikely.Secreted$Fragment==0,1]


data.frame(Curated.All = nrow(curated.Secreted),
           Curated.Fragment = nrow(curated.Secreted) - length(curated.Secreted.full))


data.frame(highlyLikely.All = nrow(highlyLikely.Secreted),
           highlyLikely.Fragment = nrow(highlyLikely.Secreted) - length(highlyLikely.Secreted.full))


data.frame(Likely.All = nrow(Likely.Secreted),
           Likely.Fragment = nrow(Likely.Secreted) - length(Likely.Secreted.full))

data.frame(weaklyLikely.All = nrow(weaklyLikely.Secreted),
           weaklyLikely.Fragment = nrow(weaklyLikely.Secreted) - length(weaklyLikely.Secreted.full))

```


HPA sometimes mentions multiple protein accessions for the same gene: these were put into separate rows

```{r }
HPA.secr.proteins <- HPA.secr[,c("Gene", "Uniprot")]

for (i in 1:nrow(HPA.secr.proteins)){
  if (grepl(",", HPA.secr.proteins$Uniprot[i], fixed=T)){
    #cutted <- strsplit(HPA.secr.proteins$Uniprot[i], split="")[[1]]
    #print(grep(",", cutted))
    proteins <- strsplit(HPA.secr.proteins$Uniprot[i], split=", ", fixed = T)[[1]]
    HPA.secr.proteins$Uniprot[i] <- proteins[1]
    # rbind(df, setNames(de, names(df)))
    
    newrow <- data.frame(HPA.secr.proteins$Gene[i], proteins[2])
    
    HPA.secr.proteins <- rbind(HPA.secr.proteins, setNames(newrow, names(HPA.secr.proteins)))
  }
}
```


Only SPromeDB entails isoforms; thus, the isoform part of the accession was removed (-1, -2 etc) to only keep the canonical accessions.

```{r }
SPRomeDB.proteins <- SPRomeDB[,c("UniProt_ID")]
SPRomeDB.proteins <- unique(unlist(lapply(SPRomeDB.proteins, function(x){strsplit(x,";", fixed=T)[[1]][1]})))
SPRomeDB.proteins.can <- unique(unlist(lapply(SPRomeDB.proteins, function(x){strsplit(x, "-", fixed=T)[[1]][1]})))
grep("-", SPRomeDB.proteins.can, fixed=T)
```

As MetazSecKB also categorizes the proteins based on strength of evidence, I kept this information in the table. However, weakly likely secreted proteins were almost never Tier 1 or 2.


```{r }

MetazSecKB.secr.proteins <- c(curated.Secreted.full, highlyLikely.Secreted.full, Likely.Secreted.full, weaklyLikely.Secreted.full)

MetazSecKB.secr.proteins.Tier <- c(rep("curated",length(curated.Secreted.full)),
                                   rep("highlyLikely",length(highlyLikely.Secreted.full)),
                                   rep("Likely",length(Likely.Secreted.full)),
                                   rep("weaklyLikely",length(weaklyLikely.Secreted.full)))
names(MetazSecKB.secr.proteins.Tier) <- MetazSecKB.secr.proteins


```

In summary, 15728 proteins will be present in the summarized secreted protein table based on the 3 databases.

```{r }
secreted.proteins.can <- unique(c(HPA.secr.proteins$Uniprot, MetazSecKB.secr.proteins, SPRomeDB.proteins.can))
secreted.proteins.can <- secreted.proteins.can[secreted.proteins.can!=""]
secreted.proteins.can <- secreted.proteins.can[secreted.proteins.can!="NA"]

length(secreted.proteins.can)
```
# Creating and exporting the summarized secreted protein table


```{r }
All.Secreted.proteins <- as.data.frame(matrix(nrow=length(secreted.proteins.can), ncol=4))
row.names(All.Secreted.proteins) <-secreted.proteins.can
colnames(All.Secreted.proteins) <- c("HPA", "MetazSecKB","MetazSecKB_Category", "SPRomeDB")

for (i in 1:nrow(All.Secreted.proteins)){
  All.Secreted.proteins[i,1] <- ifelse(row.names(All.Secreted.proteins)[i] %in% HPA.secr.proteins$Uniprot, "*", "")
  All.Secreted.proteins[i,2] <- ifelse(row.names(All.Secreted.proteins)[i] %in% MetazSecKB.secr.proteins, "*", "")
  All.Secreted.proteins[i,4] <- ifelse(row.names(All.Secreted.proteins)[i] %in% SPRomeDB.proteins.can, "*", "")
  All.Secreted.proteins[i,3] <- MetazSecKB.secr.proteins.Tier[row.names(All.Secreted.proteins)[i]]
}

All.Secreted.proteins$Present <- paste(All.Secreted.proteins$HPA, All.Secreted.proteins$MetazSecKB, All.Secreted.proteins$SPRomeDB, sep="")

for (i in 1:nrow(All.Secreted.proteins)){
  if (All.Secreted.proteins$Present[i] == "***"){
    All.Secreted.proteins$Tier[i] <- "1"
  } else if (All.Secreted.proteins$Present[i] == "**"){
    All.Secreted.proteins$Tier[i] <- "2"
  } else if (All.Secreted.proteins$Present[i] == "*"){
    All.Secreted.proteins$Tier[i] <- "3"
  }
}

All.Secreted.proteins$Protein <- row.names(All.Secreted.proteins)

All.Secreted.proteins <- All.Secreted.proteins[,c("Protein", "Tier", "HPA", "SPRomeDB", "MetazSecKB", "MetazSecKB_Category")]
All.Secreted.proteins <- All.Secreted.proteins[order(All.Secreted.proteins$Tier),]


```

Export this protein secretion info table (Secreted_Protein_Table_HPA_MetazSecKB_SPRomeDB.txt) for future use:

```{r }
Only.secreted <- All.Secreted.proteins[All.Secreted.proteins$Tier =="1" | All.Secreted.proteins$Tier =="2","Protein"]
```



```{r ,eval=F}

export_with_rowname(All.Secreted.proteins, "Files/Secreted_Protein_Table_HPA_MetazSecKB_SPRomeDB", F)

export_with_rowname(Only.secreted, "Files/Tier1_and_2_secreted", F)


```



# Visualize the Tier 1-4 proteins



```{r }
CP.expr <- read_in_with_rowname("Files/CP_expression_full",F)
CM.expr <- read_in_with_rowname("Files/CM_expression_full",F)

SD.CP <- apply(CP.expr, 1, sd, na.rm=TRUE)
SD.CM <- apply(CM.expr, 1, sd, na.rm=TRUE)

Mean.CP <- apply(CP.expr, 1, mean, na.rm=TRUE)
Mean.CM <- apply(CM.expr, 1, mean, na.rm=TRUE)

VVs.CP <- apply(CP.expr, 1, function(x){sum(!is.na(x))})
VVs.CM <- apply(CM.expr, 1, function(x){sum(!is.na(x))})

secr <- read_in_with_rowname("Files/Tier1_and_2_secreted",F)[,1]

```



```{r }
SD.dataframe <- data.frame(Protein = unique( c(row.names(CP.expr), row.names(CM.expr))))

for (i in 1:nrow(SD.dataframe)){
  SD.dataframe$CP.SD[i] <- SD.CP[SD.dataframe$Protein[i]]
  SD.dataframe$CM.SD[i] <- SD.CM[SD.dataframe$Protein[i]]
  
  SD.dataframe$CP.Mean[i] <- Mean.CP[SD.dataframe$Protein[i]]
  SD.dataframe$CM.Mean[i] <- Mean.CM[SD.dataframe$Protein[i]]
  
  if (SD.dataframe$Protein[i] %in% All.Secreted.proteins$Protein){
    secrInfo <- All.Secreted.proteins[All.Secreted.proteins$Protein == SD.dataframe$Protein[i],"Tier"]
  } else {
    secrInfo <- "4"
  }
  
  SD.dataframe$Secretion_info[i] <- secrInfo
  
  
  SD.dataframe$CP.VVs[i] <- VVs.CP[SD.dataframe$Protein[i]]
  SD.dataframe$CM.VVs[i] <- VVs.CM[SD.dataframe$Protein[i]]
}

```



```{r , fig.width=10, fig.height=5}

g1 <- ggplot(SD.dataframe, aes(x=Secretion_info, y=CP.VVs)) +
  geom_boxplot()+ theme_bw()+scale_fill_brewer(palette="Set1")+
  xlab("Secretion Tier") + ylab("#Valid values across samples") + ggtitle("CP")

g2 <- ggplot(SD.dataframe, aes(x=Secretion_info, y=CM.VVs)) +
  geom_boxplot()+ theme_bw()+scale_fill_brewer(palette="Set1")+
  xlab("Secretion Tier") + ylab("#Valid values across samples") + ggtitle("CM")

ggarrange(g1, g2)

```



```{r , fig.width=10, fig.height=6}


p <- ggplot(SD.dataframe, aes(x = CP.Mean, y = CP.SD)) +
    geom_point(alpha=0.5,aes(color = Secretion_info))+ theme_classic() + 
  theme(legend.position = "bottom") + ggtitle("CP") + 
  xlab("Protein mean intensity") + ylab("Protein standard deviation")+
  scale_colour_manual( values=c("1" = "red", "2" = "blue", "3" = "lightgreen", "4" = "grey"))+
  xlim(c(9, 33)) + ylim(c(0,5.5))
p1 <- ggExtra::ggMarginal(p, type = "density", groupFill  = TRUE)


p <- ggplot(SD.dataframe, aes(x = CM.Mean, y = CM.SD)) +
    geom_point(alpha=0.5,aes(color = Secretion_info))+ theme_classic() + 
  theme(legend.position = "bottom")  + ggtitle("CM") + 
  xlab("Protein mean intensity") + ylab("Protein standard deviation")+
  scale_colour_manual( values=c("1" = "red", "2" = "blue", "3" = "lightgreen", "4" = "grey"))+
  xlim(c(9, 33)) + ylim(c(0,5.5))
p2 <- ggExtra::ggMarginal(p, type = "density", groupFill  = TRUE)

ggarrange(p1,p2, ncol=2)

```



```{r Export RData for figure}
Fig_secreted <- SD.dataframe
save(Fig_secreted, file="RData/Fig_secreted.RData")
```


